% 03_group_info.tex
\section{Task Assignment}


Below is the detailed task assignment for each member of the group.


\begin{center}
\renewcommand{\arraystretch}{1.5} % Tăng khoảng cách giữa các hàng cho thoáng mắt
\begin{longtable}{|c|c|p{3.2cm}|p{6.5cm}|c|}
\hline
\textbf{No.} & \textbf{Student ID} & \textbf{Name} & \textbf{Task} & \textbf{Hours} \\ \hline
\endfirsthead


\multicolumn{5}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline
\textbf{No.} & \textbf{Student ID} & \textbf{Name} & \textbf{Task} & \textbf{Hours} \\ \hline
\endhead


\hline \multicolumn{5}{|r|}{{Continued on next page}} \\ \hline
\endfoot


\hline
\endlastfoot


1 & 25125014 & Nguyễn Đức Huy & Write a generic file parser in the Controller that reads an external text file and returns a standard array/vector of strings or integers. & 4.25 \\ \hline
2 & 25125014 & Nguyễn Đức Huy & Implement logic to generate randomized data arrays, including the optimization of the random DAG algorithm to prevent dense graphing. & 13 \\ \hline
3 & 25125014 & Nguyễn Đức Huy & Implement and wire the UI keyboard entry logic to directly capture and convert user inputs into data arrays within AppEngine's DataManager. & 18.5 \\ \hline
4 & 25125014 & Nguyễn Đức Huy & Ensure empty data structures are safely handled if no input data is provided. & 2.25 \\ \hline
5 & 25125014 & Nguyễn Đức Huy & Enforce Git rules: Review PRs, ensure the commit list is growing, and verify every single struct/class has exactly 2 files (.h and .cpp). & 4.5 \\ \hline
6 & 25125014 & Nguyễn Đức Huy & Implement MinHeap and MaxHeap classes inheriting from the base IHeapStructure. & 6.5 \\ \hline
7 & 25125014 & Nguyễn Đức Huy & Develop zero-based index arithmetic logic for parent-child relationships within the 1D array. & 2.25 \\ \hline
8 & 25125014 & Nguyễn Đức Huy & Implement Reheap Up and Reheap Down (bubbling) mechanics, capturing each element swap as a Frame in the Timeline. & 4 \\ \hline
9 & 25125014 & Nguyễn Đức Huy & Add missing pseudocode for Heap operations and synchronize the execution highlights with the visual state. & 4.25 \\ \hline
10 & 25125014 & Nguyễn Đức Huy & Implement AVL Tree node insertion and deletion logic alongside dynamic height updates. & 8.5 \\ \hline
11 & 25125014 & Nguyễn Đức Huy & Implement recursive balancing logic and the four fundamental rotation types (Left, Right, Left-Right, Right-Left). & 2.25 \\ \hline
12 & 25125014 & Nguyễn Đức Huy & Extract each discrete step of the pointer rotation adjustments into TreePayload frames for accurate Renderer animation. & 4.25 \\ \hline
13 & 25125014 & Nguyễn Đức Huy & Add missing pseudocode for AVL tree operations to clearly indicate when a rotation is triggered. & 4.25 \\ \hline
14 & 25125014 & Nguyễn Đức Huy & Ensure the 2D camera viewport smoothly resets and centers only upon initialization of a new data structure. & 12.75 \\ \hline
15 & 25125014 & Nguyễn Đức Huy & Replace heap-based AVL rendering with a compact layout for better space efficiency. & 3 \\ \hline
16 & 25125074 & Nguyễn Anh Kiệt & Write the report document for group work & 1 \\ \hline
17 & 25125074 & Nguyễn Anh Kiệt & Write the introduction for the report. & 1 \\ \hline
18 & 25125074 & Nguyễn Anh Kiệt & Ensure the 2D camera viewport smoothly resets and centers only upon initialization of a new data structure. & 3 \\ \hline
19 & 25125074 & Nguyễn Anh Kiệt & Initialize and configure the core application window setup. & 4 \\ \hline
20 & 25125074 & Nguyễn Anh Kiệt & Implement the basic system (managing colors, fonts, and dimensions). & 5 \\ \hline
21 & 25125074 & Nguyễn Anh Kiệt & Develop rendering functions for Nodes and Array Cells based on target coordinates. & 5 \\ \hline
22 & 25125074 & Nguyễn Anh Kiệt & Develop rendering functions for directed (arrowed) and undirected lines based on positions. & 8 \\ \hline
23 & 25125074 & Nguyễn Anh Kiệt & Develop text rendering functions at specified positional coordinates. & 4 \\ \hline
24 & 25125074 & Nguyễn Anh Kiệt & Handle application window resizing logic and fullscreen mode toggling. & 4 \\ \hline
25 & 25125074 & Nguyễn Anh Kiệt & Integrate state messaging (wire messages) during data structure visualization. & 9 \\ \hline
26 & 25125074 & Nguyễn Anh Kiệt & Implement data structure animations utilizing Lerp and Spring physics. & 10 \\ \hline
27 & 25125074 & Nguyễn Anh Kiệt & Upgrade visual effects and interactions for UI components (e.g., buttons, speed sliders). & 9 \\ \hline
28 & 25125074 & Nguyễn Anh Kiệt & Implement dynamic visual effects for the application background. & 4 \\ \hline
29 & 25125074 & Nguyễn Anh Kiệt & Develop tracing effects for algorithm execution paths and pseudocode highlighting. & 11 \\ \hline
30 & 25125074 & Nguyễn Anh Kiệt & Design and implement decorative graphics for menus within payload functions. & 4 \\ \hline
31 & 25125074 & Nguyễn Anh Kiệt & Add animations for canvas interactions & 8 \\ \hline
32 & 25125074 & Nguyễn Anh Kiệt & Create visual illustrations of various data structures for user reference. & 5 \\ \hline
33 & 25125045 & Trần Như Khải & Produce and edit the official project demonstration video & 2 \\ \hline
34 & 25125045 & Trần Như Khải & Develop and manage the overall Graphical User Interface (GUI) system utilizing the ImGui library & 5 \\ \hline
35 & 25125045 & Trần Như Khải & Implement Navigation Menu & 2 \\ \hline
36 & 25125045 & Trần Như Khải & Implement global UI controls, including dynamic Light/Dark theme toggling and Home navigation. & 3 \\ \hline
37 & 25125045 & Trần Như Khải & Architect a reusable Button class & 7 \\ \hline
38 & 25125045 & Trần Như Khải & Develop a modular Slider class & 13 \\ \hline
39 & 25125045 & Trần Như Khải & Engineer dynamic Input Menus to facilitate user data entry and structural manipulation. & 20 \\ \hline
40 & 25125045 & Trần Như Khải & Design and implement the Real-time Pseudocode Tracking Panel. & 5 \\ \hline
41 & 25125045 & Trần Như Khải & Integrate various UI modules into the UIManager and implement communication interfaces to synchronize visual states with the back-end logic. & 15 \\ \hline
42 & 25125045 & Trần Như Khải & Provide technical support for identifying and resolving front-end rendering bugs. & 15 \\ \hline
43 & 25125083 & Nguyễn Đình Minh Huy & Designed the initial MVC (Model-View-Controller) folder architecture for the project. & 4 \\ \hline
44 & 25125083 & Nguyễn Đình Minh Huy & Configured the cross-platform CMake build environment, created compile\_commands.json generation logic to ensure code editors and IDEs understand the codebase. & 1 \\ \hline
45 & 25125083 & Nguyễn Đình Minh Huy & Created the LaTeX templates and structure for the ongoing project reports. Authored the README.md and PHASE1\_TASKS.md documentation & 1 \\ \hline
46 & 25125083 & Nguyễn Đình Minh Huy & Designed the base IVisualizable into (originally IDataStructure) to enforce standard methods across models. & 2 \\ \hline
47 & 25125083 & Nguyễn Đình Minh Huy & Refactored IDataStructure into specialized sub-interfaces: IStandardStructure, IHeapStructure, and IGraphStructure (GridGraph inherits IVisualizable directly) to accomodate diverse inputs. & 6 \\ \hline
48 & 25125083 & Nguyễn Đình Minh Huy & Executed a codebase-wide refactoring to convert all indices from int to size\_t, preventing overflow and ensuring memory compatibility. & 2 \\ \hline
49 & 25125083 & Nguyễn Đình Minh Huy & Implemented the Visitor Design Pattern within the Model and View layers to cleanly decouple IPayload generation from Renderer logic. & 10 \\ \hline
50 & 25125083 & Nguyễn Đình Minh Huy & Refactored Frame to support complex payloads (GraphPayload, TreePayload, etc) while preventing circular dependencies with edge structures. & 6 \\ \hline
51 & 25125083 & Nguyễn Đình Minh Huy & Fixed critical encapsulation leaks in the Frame and Timeline classes by enforcing private variables and explicit getter/setters. & 1 \\ \hline
52 & 25125083 & Nguyễn Đình Minh Huy & Implemented the Timeline class to hold sequences of states, then engineered the Playback controller to process the Timeline and manage time-stepped traversal (Play, Pause, Step Forward, Step Backward). & 1 \\ \hline
53 & 25125083 & Nguyễn Đình Minh Huy & Implemented the AppEngine class acting as the central coordinator, then integrated the Model, UIManager, and Renderer together into the main AppEngine application loop. & 5 \\ \hline
54 & 25125083 & Nguyễn Đình Minh Huy & Fixed the ImGui-SFML initialization and shutdown lifecycle to resolve teardown assertions and crashes during application exit. & 3 \\ \hline
55 & 25125083 & Nguyễn Đình Minh Huy & Upgraded error messaging for better debugging processes. & 1 \\ \hline
56 & 25125083 & Nguyễn Đình Minh Huy & Implemented the core logic and algorithms for SinglyLinkedList. & 2 \\ \hline
57 & 25125083 & Nguyễn Đình Minh Huy & Implemented the core logic for the AdjacencyMatrix and AdjacencyList graph structure. & 4 \\ \hline
58 & 25125083 & Nguyễn Đình Minh Huy & Implemented the GridGraph structure specifically for grid-based pathfinding visualizations. & 2 \\ \hline
59 & 25125083 & Nguyễn Đình Minh Huy & Implemented the physics layout graph generator and upgraded to produce better clustering resolution. & 6 \\ \hline
60 & 25125083 & Nguyễn Đình Minh Huy & Implemented Graph algorithms (Dijkstra, A*, Bellman-Ford, Floyd-Warshall, Johnson) & 10 \\ \hline
61 & 25125083 & Nguyễn Đình Minh Huy & Implemented Grid specialized algorithms (BFS, A*) & 4 \\ \hline
62 & 25125083 & Nguyễn Đình Minh Huy & Introduced the PseudocodeManager class to act as a database for algorithm codes. & 1 \\ \hline
63 & 25125083 & Nguyễn Đình Minh Huy & Wrote textual pseudocode mappings for the Singly Linked List operations and all Shortest Path algorithms. & 20 \\ \hline
64 & 25125083 & Nguyễn Đình Minh Huy & Wired the active code line indices from the running algorithm directly to the PseudocodeManager to trigger UI highlights in ImGui. & 9 \\ \hline
65 & 25125083 & Nguyễn Đình Minh Huy & Executed a massive syntax refactoring across 7+ UI components (Button, Slider, InputMenu, CodePanel, etc) for maintainability. & 5 \\ \hline
66 & 25125083 & Nguyễn Đình Minh Huy & Centralized the Theme configurations, replacing hardcoded colors/dimensions across the view components with the Theme class. & 5 \\ \hline
67 & 25125083 & Nguyễn Đình Minh Huy & Established Git branch naming conventions and team collaboration rules, managed the project timeline for Phase 1 (Framework) and Phase 2 (GUI Prototypes). & 2 \\ \hline
68 & 25125083 & Nguyễn Đình Minh Huy & Regularly reviewed Pull Requests (PRs) from team members, performed Git conflict resolutions during complex merges into the dev branch. & 30 \\ \hline
69 & 25125083 & Nguyễn Đình Minh Huy & Checked and formatted the weekly team reports for completeness and consistency (Weeks 04 through 09). & 6 \\ \hline
70 & 25125083 & Nguyễn Đình Minh Huy & Wrote comments for all files & 1 \\ \hline
\end{longtable}
\end{center}


\textit{*Note: For a summarized total of task hours and GitHub link, please refer to the \textbf{Summary} section at the beginning of this document. For detailed Git commit history, please refer to the \textbf{Appendix}.}
