% 06_implementation.tex
\section{Implementation}

This section details the concrete implementation of the core components within the system architecture. It outlines the specific mechanisms used in the Controller and Model layers, focusing on application orchestration, playback state management, and the underlying data structures utilized for visualizations.

\subsection{Controller Layer Implementation}

The Controller layer acts as the nervous system of the application, bridging user interactions with underlying structural logic and managing the flow of time.

\subsubsection{\texttt{AppEngine} (Application Orchestrator)}
The \texttt{AppEngine} class encapsulates the primary SFML event loop and coordinates all subsystems. Its implementation handles several critical responsibilities:

\begin{itemize}
    \item \textbf{Input Event Processing}: The \texttt{AppEngine} captures standard SFML events. If an event is not consumed by the \texttt{UIManager} (e.g., Dear ImGui captures a click on a menu button), it falls back to the \texttt{Renderer}. This allows seamless interaction, such as dragging and dropping graph nodes directly on the canvas without triggering UI elements.
    \item \textbf{View Manipulation (Zoom and Pan)}: To handle large data structures, \texttt{AppEngine} implements an interactive 2D camera system. Mouse scroll wheel events dynamically scale the \texttt{sf::View}, adjusting the zoom factor with clamped boundaries to prevent extreme scaling. Panning is implemented by tracking the mouse delta between \texttt{MouseButtonPressed} and \texttt{MouseMoved} events and shifting the \texttt{sf::View} center accordingly.
    \item \textbf{Data Action Routing}: When a user requests an algorithm (e.g., Insert, Delete, Run A*), \texttt{AppEngine} queries the \texttt{UIManager} for the input parameters. It then resolves the required action to a specific \texttt{AlgorithmType}, retrieves the corresponding pseudocode via \texttt{PseudocodeManager}, and dispatches the command to the active \texttt{IVisualizable} instance. Once the Model generates a \texttt{Timeline}, it is immediately assigned to the \texttt{Playback} system.
\end{itemize}

\subsubsection{\texttt{Playback} (Timeline Management)}
The \texttt{Playback} system provides VCR-like controls (Play, Pause, Step Forward, Step Backward) over the generated visualization states.
Instead of calculating animations on the fly, the \texttt{Playback} class acts as an iterator over a fully populated \texttt{Timeline}. Its \texttt{update(float deltaTime)} method tracks an internal \texttt{timeAccumulator}. When the accumulator exceeds the \texttt{baseStepDuration} (modified by a \texttt{speedMultiplier}), the system advances to the next \texttt{Frame} in the timeline. This design guarantees deterministic animation and allows users to jump instantly to any step in the algorithm's execution without recalculating the model's state.

\subsection{Model Layer Implementation}

The Model layer houses the mathematical logic and the data payload generation mechanisms for the visualizer.

\subsubsection{Singly Linked List}
The \texttt{SinglyLinkedList} class implements the \texttt{IStandardStructure} interface. Internally, it manages a standard chain of \texttt{Node} pointers.
\begin{itemize}
    \item \textbf{Payload Generation}: Every modification or traversal step in an algorithm (like insertion or searching) records a \texttt{Frame}. The structure captures its current state into a \texttt{std::vector<int>} and creates a \texttt{LinkedListPayload}. It also attaches an array of highlighted indices.
    \item \textbf{Algorithm Tracking}: For instance, during a search operation, the list iterates through its nodes. At each node, a \texttt{Frame} is generated with the current node's index highlighted and a descriptive message (e.g., "Comparing with node value X"). This provides the View with the exact context needed to highlight the corresponding visual node on the screen.
\end{itemize}

\subsubsection{Graph Structures (Adjacency List \& Adjacency Matrix)}
Graphs are implemented using the \texttt{IGraphStructure} abstraction, with concrete variants for Adjacency Lists (optimizing sparse graphs) and Adjacency Matrices (optimizing dense graphs).
\begin{itemize}
    \item \textbf{Edge and Vertex Management}: Both variants support adding/removing vertices and directed/undirected edges with weights.
    \item \textbf{Pathfinding Algorithms}: Implementations for algorithms such as Dijkstra, Bellman-Ford, and A* are provided. During execution, the graph maps its internal state (visited nodes, current paths, edge weights) into a generic \texttt{GraphPayload}. Nodes and edges that are actively being evaluated are tagged with highlight flags within the payload, allowing the \texttt{Renderer} to change their colors dynamically.
\end{itemize}

\subsubsection{Grid Graph (Pathfinding Grids)}
The \texttt{GridGraph} structure simulates shortest-path algorithms (BFS, A*) on a 2D matrix, treating each cell as a node with implicit edges to its orthogonal and diagonal neighbors.
\begin{itemize}
    \item \textbf{State Mapping}: The grid is represented by an array of \texttt{CellState} enums (Empty, Wall, Start, End, Path, Visited).
    \item \textbf{Algorithm Visualization}: When running A*, the algorithm maintains open and closed sets. At each expansion step, a \texttt{GridPayload} is generated. Cells in the open set are marked as 'Discovered', and the current shortest path is traced backward from the current node to the start node, marked as 'Path'. This allows users to visually comprehend the expanding frontier of the heuristic search.
\end{itemize}

\subsubsection{Binary Heap}
The \texttt{BinaryHeap} implementation provides a visualization of priority queue operations, utilizing a hybrid representation that bridges a logical complete binary tree with a physical contiguous array.

\begin{itemize}
    \item \textbf{Internal Representation}: The structure is managed via \texttt{std::vector<int> heapArray}. The parent-child relationships are calculated using zero-based indexing arithmetic: a node at index $i$ has children at $2i+1$ and $2i+2$, while its parent resides at $\lfloor(i-1)/2\rfloor$.
    \item \textbf{Heapify Mechanics}: The core logic is encapsulated in \texttt{shiftUp} and \texttt{heapify} (shift-down) methods. During an \texttt{insert} or \texttt{remove} operation, every swap between elements triggers the generation of a new \texttt{Frame}. This allows the \texttt{Renderer} to animate the "bubbling" effect of elements moving through the levels of the tree.
    \item \textbf{Polymorphic Comparison}: Through the \texttt{IHeapStructure} abstraction, the system supports both \texttt{MinHeap} and \texttt{MaxHeap}. The specific heap property is enforced by overriding the pure virtual \texttt{compare()} method, which determines the priority during the restoration of the heap invariant.
\end{itemize}

\subsubsection{AVL Tree (Self-Balancing BST)}
The \texttt{AVLTree} implementation focuses on demonstrating the maintenance of the height-balance property ($|balance\_factor| \leq 1$) through recursive rotations.

\begin{itemize}
    \item \textbf{Recursive Balancing}: The structure uses a nested \texttt{Node} structure containing \texttt{height} and pointer-based child references. Following every \texttt{insert} or \texttt{remove} operation, the algorithm recursively traverses back to the root, updating heights and invoking the \texttt{balance()} method.
    \item \textbf{Rotation Visualization}: The four types of rotations (Left, Right, Left-Right, and Right-Left) are decomposed into discrete steps. When a rotation occurs, the \texttt{AVLTree} generates a \texttt{TreePayload} that updates the parent-child pointers and node positions. The \texttt{Timeline} captures the transient states where the balance factor is violated, highlighting the specific nodes that trigger the rotation logic.
    \item \textbf{Payload Mapping}: To facilitate rendering, the tree structure is flattened into a \texttt{TreePayload} containing \texttt{TreeNodeData} objects. Each node is assigned a unique ID and its current height, which the \texttt{Renderer} uses to compute the geometric layout on the 2D canvas, ensuring that subtrees do not overlap visually.
\end{itemize}

\subsection{View Layer Implementation}

The View layer is responsible for the visual representation of data structures and the management of user interactions. It adopts a dual-platform approach: utilizing the Simple and Fast Multimedia Library (SFML) for high-performance 2D canvas rendering, and Dear ImGui for immediate-mode overlay interfaces.

\subsubsection{\texttt{UIManager} (The Mediator)}
To prevent tight coupling between the graphical interface and the core algorithmic logic, the system employs the \texttt{UIManager} class acting as a Mediator.
\begin{itemize}
    \item \textbf{Centralized UI Aggregation}: Instead of exposing individual UI components to the engine, \texttt{UIManager} encapsulates the \texttt{NavigationMenu}, \texttt{InputMenu}, \texttt{CodePanel}, and all playback widgets (\texttt{Button}, \texttt{Slider}).
    \item \textbf{State Synchronization}: The interface does not process logic; it merely polls user commands (e.g., \texttt{getInputAction()}, \texttt{getInputString1()}) and relays them to the \texttt{AppEngine}. Conversely, the engine updates the UI via the \texttt{syncPlaybackUI()} method, ensuring that buttons correctly reflect the current timeline state (e.g., disabling the 'Step Forward' button when the algorithm terminates).
\end{itemize}

\subsubsection{\texttt{Renderer} (The Visitor Pattern)}
The \texttt{Renderer} class is dedicated to drawing the algorithmic payloads onto the SFML canvas. It explicitly implements the \texttt{IPayloadVisitor} interface, leveraging the Visitor design pattern.
\begin{itemize}
    \item \textbf{Polymorphic Rendering}: When the core generates a visual state, it passes a generic payload to the \texttt{Renderer}. Through overloaded \texttt{visit()} methods, the \texttt{Renderer} dynamically resolves the payload type (e.g., \texttt{TreePayload}, \texttt{GraphPayload}) and invokes the appropriate drawing subroutines.
    \item \textbf{Geometric Calculations}: The renderer abstracts complex SFML draw calls into reusable functions like \texttt{drawImageNode()} and \texttt{drawLineWithArrow()}, mathematically calculating boundary points based on the shape types (Circle or Rectangle) to ensure arrows precisely touch the edges of the nodes without overlapping.
\end{itemize}

\subsubsection{Dynamic Theming and Custom Animations}
To enhance the user experience, the system avoids static styling by implementing a global \texttt{Theme} singleton.
\begin{itemize}
    \item \textbf{On-the-fly Customization}: The \texttt{Theme} structure holds global configurations for colors, typography, and asset paths, enabling seamless toggling between Dark and Light modes without requiring an application restart.
    \item \textbf{Advanced ImGui Widgets}: Moving beyond default ImGui components, the \texttt{UIanimation} namespace introduces custom, mathematically interpolated widgets. Functions such as \texttt{JuicySliderFloat()} and \texttt{CyberButton()} utilize linear interpolation (Lerp) to create smooth scaling, pulsing glows, and dynamic color transitions, providing a highly polished, modern interface.
\end{itemize}

\subsection{Animation System}

The animation system in the project is designed to be completely frame-independent, relying heavily on the \texttt{DeltaTime} ($\Delta t$) parameter. Instead of abruptly changing states, all transitions regarding coordinates, scale, and colors are computed via continuous mathematical functions, yielding a highly fluid visual experience (Game Feel).

The system is divided into four main components: Mathematical Foundations, Data Structure Animations, UI Animations, and Cinematic Menu Decorations.

\subsubsection{Mathematical Foundations}

\paragraph{Non-linear Interpolation (Exponential Decay Lerp)} 
To ensure objects move smoothly to their targets without stuttering upon sudden direction changes, the project employs an interpolation formula with an exponentially decaying weight rather than a traditional linear Lerp:

\begin{equation} 
    V_{current} = V_{current} + (V_{target} - V_{current}) \times \left(1 - e^{-k \cdot \Delta t}\right) 
\end{equation}

Where: 
\begin{itemize} 
    \item $V_{current}$: The current value (position, scale, RGB color). 
    \item $V_{target}$: The target value. 
    \item $k$: The convergence rate constant (e.g., $k = 15.0$ for translation, $k = 10.0$ for color transition). 
    \item $\Delta t$: The elapsed time between two frames. 
\end{itemize}

\paragraph{Sinusoidal Waves for Continuous Motion} 
Continuous oscillating effects, such as pulsing glows, floating motions, and glitch noises, are driven by trigonometric functions based on real-time (\texttt{appTime}):

\begin{equation} 
    y = A \cdot \sin(\omega \cdot t + \phi) 
\end{equation} 
Where $A$ is the amplitude, $\omega$ is the angular frequency, and $\phi$ is the initial phase (often dependent on the object's \texttt{index} to create a cascading delay effect).

\subsubsection{Data Structure Animations} 
The rendering process does not fetch mathematical coordinates directly. Instead, each node is managed by an isolated state structure \texttt{NodeAnimState}:

\begin{lstlisting}[language=C++, caption={Animation State Management Structure}, label={lst:node_anim}] 
struct NodeAnimState { 
    sf::Vector2f pos; 
    float scale = 0.0f; 
    float highlightAlpha = 0.0f; 
    sf::Vector2f velPos = {0.0f, 0.0f}; // For Graph physics 
    float velScale = 0.0f; 
    float colorR = -1.0f, colorG = 0.0f, colorB = 0.0f; 
}; 
\end{lstlisting}

\paragraph{Curved Paths in Trees and Heaps} 
When elements in an AVL Tree or Heap swap positions, moving them in a straight line causes visual overlap and clutter. The project resolves this by adding a perpendicular vector to the trajectory when the distance is significant:

\begin{lstlisting}[language=C++, caption={Curved Trajectory Algorithm}] 
sf::Vector2f diff = targetPos - anim.pos; 
if (std::abs(diff.x) > 1.0f || std::abs(diff.y) > 1.0f) { 
    sf::Vector2f perp(-diff.y, diff.x); // Perpendicular vector 
    anim.pos += (diff + perp * 0.3f) * lerpPos; // 0.3f is the curve factor 
} else { 
    anim.pos += diff * lerpPos; // Linear convergence when close 
} 
\end{lstlisting}

\paragraph{Spring-Damper Physics for Graphs} 
For graph structures, nodes require a realistic bouncing effect upon appearance or interaction. A physical model of tension and damping is applied:

\begin{equation} 
    \vec{v}_{new} = \left( \vec{v}_{old} + (\vec{P}_{target} - \vec{P}_{current}) \cdot \text{tension} \cdot \Delta t \right) \cdot e^{-\text{damp} \cdot \Delta t} 
\end{equation}

\begin{lstlisting}[language=C++] 
float tension = 200.0f; float damp = 12.0f; 
anim.velPos += (targetPos - anim.pos) * tension * currentDeltaTime; 
anim.velPos *= std::exp(-damp * currentDeltaTime); 
anim.pos += anim.velPos * currentDeltaTime; 
\end{lstlisting}

\subsubsection{UI Animations} 
The default ImGui interface is extremely static. To create a "Cyberpunk" aesthetic, the static library is overridden via the \texttt{UIanimation} namespace, tracking Hover and Active states independently using \texttt{ImGuiID}.

\paragraph{Particle System for Buttons} 
When interacting with buttons (e.g., Play/Pause), a burst of light particles is emitted. The system manages particle lists tied to the button's ID. Upon clicking, the algorithm spawns $15 \sim 25$ particles radiating outward at random angles:

\begin{lstlisting}[language=C++, caption={Particle Physics Update}] 
for (size_t i = 0; i < plist.size(); ) { 
    plist[i].pos += plist[i].vel * dt; // Calculate velocity 
    plist[i].vel.y += 200.0f * dt;     // Apply gravity 
    plist[i].alpha -= dt * 1.5f;       // Fade out 
    
    if (plist[i].alpha <= 0.0f) { 
        plist.erase(plist.begin() + i); // Erase dead particles 
    } else { 
        // Render particle and glowing trail 
        draw_list->AddCircleFilled(plist[i].pos, plist[i].size, pCol); 
        draw_list->AddLine(plist[i].pos,  
            plist[i].pos - ImVec2(plist[i].vel.x * 0.05f, plist[i].vel.y * 0.05f),  
            trailCol, plist[i].size); 
        ++i; 
    } 
} 
\end{lstlisting}

\paragraph{Glitch Effect (RGB Split \& Noise)} 
For hacker-styled buttons (\texttt{Glitch Button}), the system overdraws the original text with Red and Cyan channels. They are offset by a displacement calculated from combined sine and cosine functions to simulate random noise:

\begin{lstlisting}[language=C++] 
float time = (float)ImGui::GetTime(); 
float noise = std::sin(time * 45.0f) * std::cos(time * 15.0f); 
bool isGlitching = (hovered && noise > 0.5f); 

if (isGlitching) { 
    float offsetStr = 3.0f * noise; 
    // Red channel skewed right 
    draw_list->AddText(text_pos + ImVec2(offsetStr, 0), IM_COL32(255, 50, 50, 200), label); 
    // Cyan channel skewed left and down 
    draw_list->AddText(text_pos + ImVec2(-offsetStr, offsetStr * 0.5f), IM_COL32(50, 255, 255, 200), label); 
} 
\end{lstlisting}

\paragraph{Interactive Juicy Slider} 
The playback speed slider bypasses the internal ImGui behavior to calculate exact mouse coordinates, preventing crashes. Its animations include: 
\begin{itemize} 
    \item \textbf{Track Expansion:} The thickness of the track increases upon hovering. 
    \item \textbf{Shake Effect:} While dragging, the slider knob vibrates rapidly across the X and Y axes to simulate physical friction. 
    \item \textbf{Text Bump:} Whenever the speed value changes, the text string pops up abruptly and smoothly settles down via the \texttt{bumpAnim} variable. 
\end{itemize}

\subsubsection{Main Menu Cinematic Decorations} 
The background of the Main Menu incorporates highly intricate decorative animations programmed directly in SFML to maximize user immersion. These are rendered within the \texttt{DecorationPayload} and \texttt{MenuAnimPayload}.

\paragraph{Interactive Hexagon Web \& Matrix Rain} 
A honeycomb grid covers the screen. The algorithm checks the Euclidean distance from each hexagon to the mouse cursor. If the distance is within the \texttt{lightRadius}, its Alpha multiplier increases, creating a "light chasing the mouse" effect.

\begin{equation} 
    \alpha_{mouse} = 1.0 - \left( \frac{\sqrt{dx^2 + dy^2}}{R_{light}} \right) 
\end{equation} 
Simultaneously, Matrix data streams fall vertically, utilizing \texttt{std::fmod} to endlessly wrap coordinates around the screen dimensions.

\paragraph{Geometric Data Structure Emulations} 
The renderer continuously draws conceptual representations of data structures in the background, complementing the visual theme: 
\begin{itemize} 
    \item \textbf{Floating Binary Tree:} A binary tree sways back and forth using an \texttt{sf::Transform} matrix rotated by $\sin(\text{time} \cdot 0.5) \cdot 5.0^\circ$. 
    \item \textbf{Complete Graph ($K_5$):} $5$ nodes are arranged in a circle using parametric equations $(R\cos\theta, R\sin\theta)$ and are fully interconnected, while the entire graph continuously rotates. 
    \item \textbf{Wavy Linked List:} Nodes follow a horizontal sine wave path $\sin(\text{time} \cdot 3.0 + i \cdot 1.5)$. Small "data packets" travel along the edges between nodes, simulating data transfer. 
    \item \textbf{3D Isometric Matrix:} A 2D grid of squares is projected into 3D isometric space by first scaling the Y-axis by $0.6$ and then rotating the entire structure by $45^\circ$. 
    \item \textbf{Sorting Histogram:} Bar heights fluctuate using overlapping sine and cosine waves, combined with a moving "scanline" highlight effect derived from modulo operations on the bar index. 
    \item \textbf{Neural Network:} Connections between layers light up dynamically. The signal strength is calculated as $\sin(\text{time} \cdot 6.0 - \text{layer} \cdot 1.5 + n_1 \cdot 0.5 + n_2 \cdot 0.5)$. Edges with a signal $> 0.85$ are highlighted intensely. 
    \item \textbf{Central Quantum Core:} Nested elliptical orbits rotate at different speeds. A central hexagon counter-rotates, surrounded by a pulsing holographic HUD and moving barcode data streams that mimic complex processing. 
\end{itemize}