% 09_conclusion.tex
\section{Conclusion}


\subsection{Summary of Achievements}

This project successfully developed an interactive data structure visualization system that demonstrates the fundamental operations of several core data structures. The implementation integrates algorithm execution, data management, and user interface components into a cohesive architecture.

The system design separates responsibilities into distinct modules, including the algorithm engine, data management layer, and user interface controller, ensuring maintainability and scalability.

\subsection{Limitations}

Despite the achieved results, several limitations remain. First, developing a responsive and intuitive user interface using existing graphical libraries posed significant challenges. Additionally, maintaining synchronization between the user interface, data layer, and algorithm execution required careful system design.

From a functional perspective, the system currently provides limited direct interaction with data structures. Furthermore, performance and visualization clarity may degrade when handling large datasets.

\subsection{Future Work}

Future improvements will focus on expanding the range of supported data structures, including B-Trees, Tries, and Hash Tables. Enhancing user interaction is also a priority, allowing operations to be performed through direct manipulation such as mouse actions and keyboard shortcuts.

In addition, further customization options for visualization themes and node representations will be explored, along with potential optimization for handling larger datasets more efficiently.
